{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update to gpm_november2017.tex file
continue preparation of slides

\begin{frame}{2017 Top Objectives 
    12.12.2016}
  \Fontvi
\vspace{-1cm}
Objectives:
\begin{enumerate}
\item \only<2>{\color{ta3chameleon}} Provide cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$
\item \only<2>{\color{orange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor conditioon
\item \only<2>{\color{orange}}Use the new HHF probe on AUG to study
  filamentary transport under high-power H-Mode conditions and under
  different plasma configurations (SN, DN)
\item \only<2>{\color{orange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<2>{\color{orange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<2>{\color{red}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}
\onslide<2>{
  So far H-Mode operation has been limited to AUG since no operational
  scenarion in high-density NBH heated plasma on TCV has been established
}
\end{frame}

>>>>

\begin{frame}{2017 Top Objectives 
    12.12.2016}
  \Fontvi
\vspace{-1cm}
Deliverables listed during the call for manning of last December 
\begin{enumerate}
\item \only<2>{\color{ta3chameleon}} Provide cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$
\item \only<2>{\color{orange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor conditioon
\item \only<2>{\color{green}}Use the new HHF probe on AUG to study
  filamentary transport under high-power H-Mode conditions \only<2>{\color{red}}and under
  different plasma configurations (SN, DN)
\item \only<2>{\color{orange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<2>{\color{orange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<2>{\color{red}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}
\onslide<2>{
  So far H-Mode operation has been limited to AUG since no operational
  scenarion in high-density NBH heated plasma on TCV has been established
}
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PdfStructureCurrentScan_ConstantQ95}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape
      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \item<3|only@3> Still need to provide detail evolution of edge
        profiles as a function
        of $\Lambda_{div}$ which are different at different current
        although same L$_{\parallel}$
      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
        different current even though obtained at different values of $\Lambda_{div}$. 
      \item<4|only@4> Autocorrelation time $\tau_{ac}$ increases with
        $\Lambda_{div}$ without sensible difference among the current
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}
